{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-08 Paper/main.tex
KL def

	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt operator\footnote{Definitions of Hilbert-Schmidt Kernels and Operators are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

@@

	\subsection{Definition (Hilbert-Schmidt Operator)}\label{def_HS}
	Given a bounded domain $\mathcal{A} \subset \mathbb{R}^n$, we call a function $c : \mathcal{A} \times \mathcal{A} \rightarrow \mathbb{R}$ a Hilbert-Schmidt kernel if
	\begin{equation}
		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 dx dy < \infty
	\end{equation}
	where $c \in \mathbb{L}^2(\mathcal{A} \times \mathcal{A})$. Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, by

>>>>

	where the $c: [0,1] \times [0,1] \rightarrow \mathbb{R}$ are Hilbert-Schmidt Kernels and $K$ is a corresponding Hilbert-Schmidt integral operator\footnote{Definitions of Hilbert-Schmidt Kernel and Integral Operator are provided in Appendix \ref{def_HS}.} $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$ defined by
	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

@@

	\subsection{Definition (Hilbert-Schmidt Integral Operator)}\label{def_HS}
	Given a bounded domain $\mathcal{A} \subset \mathbb{R}^n$, we call a function $c : \mathcal{A} \times \mathcal{A} \rightarrow \mathbb{R}$ a Hilbert-Schmidt kernel if
	\begin{equation}
		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 dx dy < \infty
	\end{equation}
	where $c \in \mathbb{L}^2(\mathcal{A} \times \mathcal{A})$. Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, by
